Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-27 awipev-CO2.Rmd
daily diff in temp and sal between 1 and 9 m

Comparative approch allowed by following plots:

@@

Comparative approch allowed by following plots:

>>>>

### **Depth profile**

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()
summary(df)
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`). The difference with depth is therefore significant.

@@

### **Temperature profiles**
```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
#dySeries("temp_fb", color = "grey", strokeWidth = 0, label = "temp_fb") %>%
#dySeries("temp_mix", color = "black", strokeWidth = 0, label = "temp_mix") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(-2, 10)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(temp_insitu_ctd_9m, na.rm = TRUE),
            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()
summary(df)
```
There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1 and 9 m ranges between `r min(df$range)`°C and `r max(df$range)`°C (mean: `r mean(df$range)`°C; `r median(df$range)`°C). The difference with depth is therefore significant.
